Computational Document

### 2019-11-16 tutorial/01_rmarkdown/bmi_pdf.Rmd
fix hangul and pdf hangul issue

---
layout: page
title: "Computational Document"
subtitle: "체질량지수(BMI) - R마크다운(`.rmd`)"
author:
    name: 이광춘 (KPMG)
    affilates: 데이터 과학자
date: "`r Sys.Date()`"
always_allow_html: yes
output:
  html_document: 
    toc: yes
    toc_float: true
    highlight: tango
    code_folding: show
    number_section: true
    self_contained: true
editor_options: 
  chunk_output_type: console
---

@@

```{r bmi-EDA-viz}
bmi_df %>% 
  gather(키체중, 값, -Gender, -Index) %>% 
  ggplot(aes(x=Index, y= 값, fill=Gender)) +
    geom_boxplot(show.legend = FALSE) +
    facet_grid(키체중 ~ Gender,  scales="free") +
    labs(x="", y="",
         title="성별, 비만구분에 따른 키와 몸무게")
```

>>>>

---
layout: page
title: "Computational Document"
subtitle: "체질량지수(BMI) - R마크다운(`.rmd`)"
author:
    name: 이광춘 (KPMG)
    affilates: 데이터 과학자
date: "`r Sys.Date()`"
always_allow_html: yes
output:
    pdf_document :
      latex_engine : xelatex
      pandoc_args:
          - --standalone
mainfont : NanumGothic
editor_options: 
  chunk_output_type: console
---

@@

```{r bmi-EDA-viz, dev="png", dpi=400}
library(extrafont)
loadfonts()

bmi_df %>% 
  gather(키체중, 값, -Gender, -Index) %>% 
  ggplot(aes(x=Index, y= 값, fill=Gender)) +
    geom_boxplot(show.legend = FALSE) +
    facet_grid(키체중 ~ Gender,  scales="free") +
    labs(x="", y="",
         title="성별, 비만구분에 따른 키와 몸무게") +
    theme_bw(base_family="NanumGothic")
```
